Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-12-14 paper_comparison/paper_comparison/paper_comparison.Rmd
section headings

```{r}
# OOP supports needed by `visuage`
# remotes::install_github("TengMCing/bandicoot")
# 
# Visual inference models and p-value calculation
# remotes::install_github("TengMCing/visage")

@@

## Visual testing for departures

@@

### Calculating $p$-values

@@

### Power calculation

@@

# Experiment design

@@

## Simulating departures

@@

## Experiment setup

@@

## Power comparison

@@

## P-value comparison (remove?) (closer to the topic of the paper) (put it after power)

@@

## Lineup selection

>>>>

```{r}
# OOP supports needed by `visage`
# remotes::install_github("TengMCing/bandicoot")
# 
# Visual inference models and p-value calculation
# remotes::install_github("TengMCing/visage")

@@

## Visual test procedure based on lineups

@@

### Calculating $p$-values for the visual test

@@

### Power of a visual test

@@

# Experimental design

@@

## Simulating departures from good residuals

@@

## Experimental setup

@@

## Comparison of the power of different tests

@@

## Comparison of rejection rates based on $p$-values

@@

## Effect of the distribution of the independent variable

### 2022-12-14 paper_comparison/paper_comparison/paper_comparison.tex
section headings

\hypertarget{visual-testing-for-departures}{%
\subsection{Visual testing for
departures}\label{visual-testing-for-departures}}

@@

\hypertarget{calculating-p-values}{%
\subsubsection{\texorpdfstring{Calculating
\(p\)-values}{Calculating p-values}}\label{calculating-p-values}}

@@

\hypertarget{power-calculation}{%
\subsubsection{Power calculation}\label{power-calculation}}

@@

\hypertarget{experiment-design}{%
\section{Experiment design}\label{experiment-design}}

@@

\hypertarget{simulating-departures}{%
\subsection{Simulating departures}\label{simulating-departures}}

@@

\hypertarget{experiment-setup}{%
\subsection{Experiment setup}\label{experiment-setup}}

@@

\hypertarget{power-comparison}{%
\subsection{Power comparison}\label{power-comparison}}

@@

\hypertarget{p-value-comparison-remove-closer-to-the-topic-of-the-paper-put-it-after-power}{%
\subsection{P-value comparison (remove?) (closer to the topic of the
paper) (put it after
power)}\label{p-value-comparison-remove-closer-to-the-topic-of-the-paper-put-it-after-power}}

@@

\hypertarget{lineup-selection}{%
\subsection{Lineup selection}\label{lineup-selection}}

>>>>

\hypertarget{visual-test-procedure-based-on-lineups}{%
\subsection{Visual test procedure based on
lineups}\label{visual-test-procedure-based-on-lineups}}

@@

\hypertarget{calculating-p-values-for-the-visual-test}{%
\subsubsection{\texorpdfstring{Calculating \(p\)-values for the visual
test}{Calculating p-values for the visual test}}\label{calculating-p-values-for-the-visual-test}}

@@

\hypertarget{power-of-a-visual-test}{%
\subsubsection{Power of a visual test}\label{power-of-a-visual-test}}

@@

\hypertarget{experimental-design}{%
\section{Experimental design}\label{experimental-design}}

@@

\hypertarget{simulating-departures-from-good-residuals}{%
\subsection{Simulating departures from good
residuals}\label{simulating-departures-from-good-residuals}}

@@

\hypertarget{experimental-setup}{%
\subsection{Experimental setup}\label{experimental-setup}}

@@

\hypertarget{comparison-of-the-power-of-different-tests}{%
\subsection{Comparison of the power of different
tests}\label{comparison-of-the-power-of-different-tests}}

@@

\hypertarget{comparison-of-rejection-rates-based-on-p-values}{%
\subsection{\texorpdfstring{Comparison of rejection rates based on
\(p\)-values}{Comparison of rejection rates based on p-values}}\label{comparison-of-rejection-rates-based-on-p-values}}

@@

\hypertarget{effect-of-the-distribution-of-the-independent-variable}{%
\subsection{Effect of the distribution of the independent
variable}\label{effect-of-the-distribution-of-the-independent-variable}}
